Model Finding for Recursive Functions in SMT\thanks{ This research is partially supported by the Inria technological development action ``Contre-exemples utilisables par Isabelle et Coq'' (CUIC). }

### 2016-01-20 ijcar2016/body.tex
more

@@

@@

@@

\section{Examples}
\label{sec:examples}

\subsection{ANDY?}

\subsection{Lists and Lazy Lists}

\subsection{AVL Trees?}

\subsection{Huffman's Algorithm}

>>>>

TODO: Say something about admissibility for tail-recursion: Watch out if the
argument always changes...

@@

\textbf{TODO:} Mention monotonicity analysis and zero sorts.

@@

  * advantage over Nitpick:
    * generates a single problem, not parameterized by cardinalities
      * pushes all the work to the SMT solver
        * we are just starting with that -- and see lots of potential for
          optimizations and tuning

@@

\section{Case Studies}
\label{sec:case-studies}

\subsection{Lazy Lists}

XXX

\subsection{Huffman Coding}

XXX
